\thetitle

### 2021-05-20 writing/mutate-benchmarks.tex
section 6, rest

Hence, even if they do not come with type-level errors, they offer a diverse
starter suite, suitable for the careful introduction of type-level errors via
mutations. Further filtering the benchmark suite to keep the benchmarks with the
most sizeable and complex dependency graphs yields ten suitable programs while
preserving the suite's linguistic diversity. Figure~\ref{table:benchmark-descriptions} displays the selected
benchmark programs and describes their basic characteristics.

>>>>

Figure~\ref{table:benchmark-descriptions} describes the benchmark programs that
meet all the criteria and come with a sizeable and complex dependency graphs.
This additional filter is needed because Typed Racket demands type assignments
for entire modules. For benchmarks with less than five modules, finding errors
would almost be trivial.

### 2021-05-20 writing/mutate-interesting.tex
section 6, rest

The definition of interesting mutants is more than a filter for uninteresting
mutants. It is also the guide for evaluating and refining mutators until they
collectively produce a sizable and diverse population of interesting
mutants. Consider a candidate for the set of mutators that casts the tests of conditional
expressions to the {\tt Any} type, which would suppress occurrence typing. An
examination of its mutants through the lens of ``interesting'' reveals that none
of them is interesting, because they never raise run-time errors. Hence Indeed,
the interesting standard guided countless iterations of adding and removing
mutators and of refining the chosen mutators in figure~\ref{table:mutation-ops}.

>>>>

The goal of filtering for interesting mutants guided countless iterations of
adding, removing, and refining mutators in figure~\ref{table:mutation-ops}.  For
an illustrative example, Consider a candidate mutator that casts the tests of
conditionals to the {\tt Any} type. Like the example explained at the end of the
preceding subsection, this mutant would suppress occurrence typing. But, it
would not be interesting because an execution would not raise a run-time error;
instead the function would process its input as if nothing had changed. Hence
this candidate mutator is not included in the final set.

### 2021-05-20 writing/mutate-mutators.tex
Add negate-cond mutator example to section 6.2
section 6, rest

Most of the mutators are self-explanatory.  The first six apply to all
gradually typed languages; the next six to those that include classes and
objects. The last four target distinguishing features of Typed
Racket's type system,
specifically its sophisticated type system. For example, one mutation produced by {\tt arithmetic}
replaces a {\tt +} with a {\tt -} in an attempt to change the type of the
arithmetic expression; {\tt +}'s result is a {\tt Positive-Integer} when all
arguments are positive integers, while {\tt -} yields {\tt
Integer}~\citep{stathff-padl-12}. Similarly, the other three aim to confound
the occurrence type system.

>>>>

\begin{wrapfigure}{r}{.5\textwidth} \footnotesize
\hspace{0.2cm}
\begin{module}{}\typecolor
(: deal-with [(U Real False) -> Real])
(define (deal-with optional-result)
  (if optional-result
      (+ optional-result OFFSET)
      DEFAULT))

(define DEFAULT 40)
(define OFFSET  11)
\end{module}
\caption{Example program using occurrence typing}
\label{fig:negate-cond-example}
\end{wrapfigure}

Most of the mutators are self-explanatory.  The first six apply to all
gradually typed languages; the next six to those that include classes and
objects. The last four target distinguishing features of Typed Racket's type
system, specifically its sophisticated type system. For example, one mutation
produced by {\tt arithmetic} replaces a {\tt +} with a {\tt -} in an attempt to
change the type of the arithmetic expression; {\tt +}'s result is a {\tt
Positive-Integer} when all arguments are positive integers, while {\tt -}
yields {\tt Integer}~\citep{stathff-padl-12}. Similarly, the other three aim to
confound the occurrence type system. Figure~\ref{fig:negate-cond-example}
illustrates how this confusion works. The function deals with an input that is
either a {\tt Real} or {\tt \#false}; the conditional deals with the first type
in the {\tt then} branch and the second type in the {\tt else} branch.  If a
mutator wraps {\tt (not $\cdot$)} around the test of the conditional, the
resulting mutant no longer type checks and, when run, this function eventually
causes a run-time type check to signal an impedance mismatch.
